Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

\subsection{Power-performance tracing on \tintorrum}
\label{subsec:4.3}

A full tracing experiment is conducted on \tinto in order to capture an overall power
profile at a much finer resolution. First we run \cosmoart for a full-day simulation
and analyze the power consumption. Second we correlate performance with
power traces of two 1-hor time frames during the day: mid-day (from 11h-12h) and
midnight (23-24h). All the experiments were performed using 192 \cosmoart processes
mapping 12 processes in each of node.

@@

To gain insights about

>>>>

\subsection{Power-performance tracing on \tinto}
\label{subsec:4.3}

A full tracing experiment is conducted on \tinto in order to capture an overall power
profile at a much finer resolution. First we run \cosmoart for a full-day simulation
and analyze the power consumption. Second we correlate performance with
power traces of two 1-hor time frames during the day: mid-day (from 11h-12h) and
midnight (23h-24h). All the experiments were performed using 192 \cosmoart processes
mapping 12 processes in each of node.

@@

To gain more insights about the power-performance behavior of \cosmoart, we also have conducted 
experiments that show power-performance traces of 1 hour simulation. We limited the simulation 
time to this bound since the pattern of the computation performed by \cosmoart is repeated each 
hour, also because the weight of a full-day simulation trace can not be easily handled using 
our machines and memory available (about 45\,GB per trace file). To soften the problem we 
shrink the simulations to 1 hour during mid-day (11h-12h) and midnight (23h-24h), in which 
\cosmoart perform different internal computations, as shown in Figure~\ref{fig:9}. At the same
time we also leverage the two stated MPI policies: polling and waiting modes.
